---
title: "SDS315 HW 3"
author: "Samuel Li"
date: "2/12"
output: pdf_document
---

[https://github.com/SamuelLi1225/SDS_HW4](https://github.com/SamuelLi1225/SDS_HW4)

```{r setup, include=FALSE}
library(ggplot2)
library(mosaic)
library(dplyr)
knitr::opts_chunk$set(fig.height=8, fig.width=12, warning=FALSE, message=FALSE)
```
#Problem 1

```{r echo=FALSE}
library(mosaic)
set.seed(4)
simulated_results <- do(100000) * nflip(n=2021, prob = 0.024)

p_value <- mean(simulated_results >= 70)

simulated_results <- as.numeric(simulated_results[[1]])
hist(simulated_results, breaks = 50, main = "Monte Carlo Simulation of Flagged Trades", xlab = "Flagged Trades")
abline(v = 70, col = "red", lwd = 1)
```
1. Null Hypothesis: The 70 flagged trades out of 2021 from the Iron Bank employees were due to random variation. 
2. Test Statistic: The number of flagged trades in the sample of 2021 trades. 
3: Plot shown 
4: P-value is 0.00181
5. The P-value is 0.00187  which is less than 0.05, so we reject the null hyptothesis. There was likely a suspicious trade.



#Problem 2
```{r echo=FALSE}
set.seed(4)
health_simulated <- do(100000) * nflip(n=50, prob = 0.03)

health_p_value <- mean(health_simulated >= 8)
print(health_p_value)
health_simulated <- as.numeric(health_simulated[[1]])
hist(health_simulated, breaks = 12, main = "Monte Carlo simulation of Health Code Violations",xlab = "Health Code Violations")
abline(v=8, col = "red", lwd = 5)
```
1. Null Hypothesis: The 8 health code violations out of the 50 health inspections of Gourment Bites were due to random variation.
2. Test Statistic: The number of health code violtions in the sample of the 50 health inspections
3: Plot shown 
4: P-value is 0.00015
5. The P-value is 0.00015  which is less than 0.05, so we reject the null hyptothesis. There was likely health code violations.


#Problem 3
```{r echo=FALSE}
observed_counts <- c(85, 56, 59, 27, 13) 
expected_proportions <- c(0.30, 0.25, 0.20, 0.15, 0.10)  
total_jurors <- sum(observed_counts) 

expected_counts <- total_jurors * expected_proportions
print(expected_counts)

chi_test <- chisq.test(x = observed_counts, p = expected_proportions)
print(chi_test)



```
H0/Null Hypothesis: The distribution of jurors picked by the judge is unbiased. 
Test Statistic: 12.426

P-Value: 0.01445, so we reject the null hypothesis. It is likely that the judge had bias when choosing the jurors

This suggests possible existence of systematic bias in jury selection. Other explanations could be that certain races were underrepresented because of a lack of registered people or too many exemptions. 

We can investigate further by gathering more data from other judges, so that we can sample across a bigger sample size in order for a more accurate answer. 


#Problem 4


```{r echo=FALSE}
library(readr)
library(dplyr)
library(stringr)

letter_freq <- read_csv("letter_frequencies.csv")

expected_freq <- setNames(letter_freq$Probability, letter_freq$Letter)

brown_sentences <- readLines("brown_sentences.txt")

chi_squared_values <- c()

for (sentence in brown_sentences) {

  clean_sentence <- gsub("[^A-Za-z]", "", sentence) 
  clean_sentence <- toupper(clean_sentence) 
  total_letters <- nchar(clean_sentence)
  
  
  if (total_letters == 0) {
    next
  }
  
  letters <- unlist(strsplit(clean_sentence, ""))
  letter_counts <- table(letters)  # Creates a table of letter frequencies
  
  observed_counts <- rep(0, length(expected_freq))
  names(observed_counts) <- names(expected_freq)
  
  observed_counts[names(letter_counts)] <- as.numeric(letter_counts)
  
  expected_counts <- expected_freq * total_letters
  
  chi_squared <- sum((observed_counts - expected_counts)^2 / expected_counts, na.rm = TRUE)
  
  chi_squared_values <- c(chi_squared_values, chi_squared)
}

mean_chi <- mean(chi_squared_values, na.rm = TRUE)
std_dev_chi <- sd(chi_squared_values, na.rm = TRUE)
min_chi <- min(chi_squared_values, na.rm = TRUE)
max_chi <- max(chi_squared_values, na.rm = TRUE)
cat("Mean:", mean_chi, "\n")
cat("Standard Deviation:", std_dev_chi, "\n")
cat("Min:", min_chi, "\n")
cat("Max:", max_chi, "\n")



test_sentences <- c(
  "She opened the book and started to read the first chapter, eagerly anticipating what might come next.",
  "Despite the heavy rain, they decided to go for a long walk in the park, crossing the main avenue by the fountain in the center.",
  "The museum’s new exhibit features ancient artifacts from various civilizations around the world.",
  "He carefully examined the document, looking for any clues that might help solve the mystery.",
  "The students gathered in the auditorium to listen to the guest speaker’s inspiring lecture.",
  "Feeling vexed after an arduous and zany day at work, she hoped for a peaceful and quiet evening at home, cozying up after a quick dinner with some TV, or maybe a book on her upcoming visit to Auckland.",
  "The chef demonstrated how to prepare a delicious meal using only locally sourced ingredients, focusing mainly on some excellent dinner recipes from Spain.",
  "They watched the sunset from the hilltop, marveling at the beautiful array of colors in the sky.",
  "The committee reviewed the proposal and provided many points of useful feedback to improve the project’s effectiveness.",
  "Despite the challenges faced during the project, the team worked tirelessly to ensure its successful completion, resulting in a product that exceeded everyone’s expectations."
)

chi_squared_test_values <- c()

for (sentence in test_sentences) {
  
  clean_sentence <- gsub("[^A-Za-z]", "", sentence)
  clean_sentence <- toupper(clean_sentence)
  total_letters <- nchar(clean_sentence)
  
  if (total_letters == 0) {
    next
  }
  
  letters <- unlist(strsplit(clean_sentence, ""))
  letter_counts <- table(letters)
  
  observed_counts <- rep(0, length(expected_freq))
  names(observed_counts) <- names(expected_freq)
  
  observed_counts[names(letter_counts)] <- as.numeric(letter_counts)
  
  expected_counts <- expected_freq * total_letters
  
  chi_squared <- sum((observed_counts - expected_counts)^2 / expected_counts, na.rm = TRUE)
  
  chi_squared_test_values <- c(chi_squared_test_values, chi_squared)
}

p_values <- 1 - pnorm(chi_squared_test_values, mean = mean_chi, sd = std_dev_chi)

p_values_table <- data.frame(
  Sentence_ID = 1:10,
  Chi_Squared = round(chi_squared_test_values, 6),
  P_Value = round(p_values, 6)
)

print(p_values_table)
llm_sentence <- which.min(p_values)
cat("The sentence likely generated by the LLM is", llm_sentence)
```

















